MSPMS Report

### 2024-07-03 inst/rmarkdown/templates/mspms_report/skeleton/skeleton.Rmd
added download buttons

```{r}
# The standard mspms data processing pipeline is used here. 
mspms_data = mspms::mspms(prepared_data,design_matrix)
```

@@

DT::datatable(t1)
```

@@

DT::datatable(t2)
```

>>>>

```{r}
# The standard mspms data processing pipeline is used here. 
mspms_data = mspms::mspms(prepared_data,design_matrix)

mspms_data %>%
  downloadthis::download_this(
    output_name = "mspms_data",
    output_extension = ".csv",
    button_label = "Download data",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save",
    csv2 = FALSE
  )
```

@@

DT::datatable(t1)

t1 %>%
  downloadthis::download_this(
    output_name = "mspms_anova",
    output_extension = ".csv",
    button_label = "Download anova",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save",
    csv2 = FALSE
  )
```

@@

DT::datatable(t2)

t2 %>%
  downloadthis::download_this(
    output_name = "mspms_t-tests",
    output_extension = ".csv",
    button_label = "Download ttests",
    button_type = "warning",
    has_icon = TRUE,
    icon = "fa fa-save",
    csv2 = FALSE
  )
```
